Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-04 metrics.tex
Metrics and Methodology done

\subsection{Goodput}
We consider the goodput defined as the ratio of the useful delivered
information at the application layer and the total processing time. We focus
on the goodput considering only the coding process, i.e. we assume that
the application data has been properly generated before encoding and
also correctly post-processed after decoding. In this way, we define
the goodput for either an encoder or a decoder as follows:
%
\begin{align} \label{eq:goodput}
R_{proc} = \frac{gB}{T_{proc}} ~ [\mathrm{Bytes/s}]
\end{align}
%
In \eqref{eq:goodput}, $B$ and $g$ are the packet and generation size
as defined previously and both represented the data to be processed. For
goodput measurements, we are concerned in quantifying the processing time
for either encoding or decoding $g$ \ac{l.i.} packets. Thus, $T_{proc}$ is
the processing time required for this processing. In the next subsections, we
define two time bechmarks available in [\textbf{Chres repos here}].
The purpose of the benchmarks is to quantify the processing time for
any of the coding schemes considered in Section \ref{sec:schemes}.

@@

The average power specifies the rate at which energy is
consumed in the \ac{Raspi}. Thus, for a given energy value in the device
battery without any external supplies, this metric permits to infer the amount
of time for which the \ac{Raspi} can operate autonomously before draining
out its battery. For the energy per bit consumption, it indicates how
much energy is expended to effectively transmit or receive 1 bit of bit
considering the encoding or decoding respectively. This energy is computed

For our energy measurement campaign, we automate the setup presented
in Fig. \ref{fig:measurement_setup} to sequentially run a series of
simulations for a given configuration of coding scheme and parameters,
to estimate the energy consumption in both of our \ac{Raspi}
models. A representative sketch of the setup is shown in the
computer monitor in Fig. \ref{fig:measurement_setup}. The figure presents
a \ac{Raspi} device whose power supply is an Agilent 66319D \ac{DC} source,
instead of its conventional chorded supply. The output of the measurements
are later sent to a workstation where the raw measurement data is processed.
The measured variable was the current consumed by the device for a fixed
5V supply from the source. To identify each experiment, we classified the
electrical current samples into two groups based on the magnitude. In our
measurements, the groups to be reported are the idle current $I_{idle}$
and the processing current $I_{proc}$. The former is the current the
\ac{Raspi} requires while in idle state, meaning that no processing
is being carried. The latter stands for the current needed during
the encoding or decoding processing of the packets. The measurements
where $I_{proc}$ is observed are made for a given configuration of
coding scheme with its parameters. Finally, each simulation was enumerated
to map the coding speed measurements with the corresponding energy
consumption.

@@

\subsubsection{Average Power Expenditure}
To extract the energy consumption of network coding, we subtracted the
idle energy consumption from the energy consumption used during simulations.

%
\begin{align} \label{eq:avg_current}
I_{avg} = \frac{1}{N_s}\sum_{k=1}^{N_s} I_{k}  ~[\mathrm{Amperes}]
\end{align}
%

%
\begin{align} \label{eq:avg_power}
P_{avg} = V_{supply}(I_{proc,avg} - I_{idle,avg}) ~[\mathrm{Watts}]
\end{align}
%
\subsubsection{Energy per Bit Consumption}
%
\begin{align} \label{eq:goodput}
E_b = P_{avg} T_{proc} = P_{avg} \times \frac{gB}{R_{proc}} ~[\mathrm{Joules/bit}]
\end{align}
%

>>>>

\subsection{Goodput}
We consider the goodput defined as the ratio of the useful delivered
information at the application layer and the total processing time. We focus
on the goodput considering only the coding process, i.e. we assume that
the application data has been properly generated before encoding and
also correctly post-processed after decoding. In this way, we define
the goodput for either an encoder or a decoder as follows:
%
\begin{align} \label{eq:goodput}
R_{proc} = \frac{gB}{T_{proc}} ~ [\mathrm{Bytes/second}]
\end{align}
%
In \eqref{eq:goodput}, $B$ and $g$ are the packet and generation size
as defined previously and both represented the data to be processed. For
goodput measurements, we are concerned in quantifying the processing time
for either encoding or decoding $g$ \ac{l.i.} packets. Thus, $T_{proc}$ is
the processing time required for this processing. In the next subsections, we
define two time bechmarks available in [\textbf{Chres repos here}].
The purpose of the benchmarks is to quantify the processing time for
any of the coding schemes considered in Section \ref{sec:schemes}.

@@

The average power specifies the rate at which energy is
consumed in the \ac{Raspi}. Thus, for a given energy value in the device
battery without any external supplies, this metric permits to infer the amount
of time for which the \ac{Raspi} can operate autonomously before draining
out its battery. For the energy per bit consumption, it indicates how
much energy is expended to effectively transmit or receive 1 bit of bit
considering the encoding or decoding respectively.

For our energy measurement campaign, we automate the setup presented
in Fig.~\ref{fig:measurement_setup} to sequentially run a series of
simulations for a given configuration of a coding scheme and its parameters,
to estimate the energic expenditure in both of our \ac{Raspi}
models. The energy measurement setup goal is to quantify the power
consumption of the \ac{Raspi} over long periods of processing time to
obtain accurate results. A representative sketch of the setup is shown
in the computer monitor in Fig.~\ref{fig:measurement_setup}.

The energy measurement setup presents a \ac{Raspi} device whose power
supply is an Agilent 66319D \ac{DC} source, instead of a conventional
power chord supply.   To compute the power, we just need to measure
the current since the \ac{Raspi} feeds from a fixed input voltage of $5V$
set by the Agilent device, but its current consumption is variable.
Hence, the measured variable is the current consumed by the device for
this fixed input voltage. The output of the measurements
are later sent to a workstation where the raw measurement data is processed.

@@

To identify each experiment, we classified the electrical current samples
into two groups based on the magnitude. In our measurements, the groups to
be reported are the idle current $I_{idle}$ and the processing current
$I_{proc}$. The former is the current the \ac{Raspi} requires while in idle
state, meaning that no processing is being carried. The latter stands for
the current needed during the encoding or decoding processing of the packets.
Measurements are taken either when $I_{idle}$ or $I_{proc}$ are observed.
For the processing currents, its current measurements are made while the
goodput benchmarks are running for a given configuration of a coding scheme
with its parameters. For each configuration, $10^3$ simulations from the
goodput benchmarks are carried during the period of time where $I_{proc}$
occurs. We remark that a simulation is the conveying of $g$ \ac{l.i.} coded
packets. Finally, for each configuration, each set of current measurements is
enumerated to map it with its average power value and the corresponding goodput
measurements. At post-processing, from the average power expenditure and the
results from the goodput measurements it is possible to extract the energy
per bit consumption. We elaborate further on this post-processing in the
next subsections.

\subsubsection{Average Power Expenditure}
To extract the average power for a given configuration in our setup, we
first calculate the average current in each the idle state $I_{idle,avg}$
and the processing state $I_{idle,avg}$ for all the available sample for
the given configuration. Regardless of the current type, the average value
of the sample set of a given number of samples $N_s$ is:
%
\begin{align} \label{eq:avg_current}
I_{avg} = \frac{1}{N_s}\sum_{k=1}^{N_s} I_{k}  ~[\mathrm{Amperes}]
\end{align}
%
With the average current from \eqref{eq:avg_current}, we compute the average
current used for processing with respect to the idle state, by substracting
$I_{idle,avg}$ from $I_{proc,avg}$. Then, the result is multiplied by the
supply voltage to obtain the average power during the considered configuration,
given as:
%
\begin{align} \label{eq:avg_power}
P_{avg} = V_{supply}(I_{proc,avg} - I_{idle,avg}) ~[\mathrm{Watts}]
\end{align}
%
\subsubsection{Energy per Bit Consumption}
To get this metric for a given configuration, we simply express the energy
as the product of the average power by the processing time $T_{proc}$ obtained
from the goodput measurement for the same configuration. In this way, we can
relate the processing time by the goodput, the packet and the generation size
as shown:
%
\begin{align} \label{eq:goodput}
E_b = P_{avg} T_{proc} = P_{avg} \times \frac{g(B/8)}{R_{proc}} ~[\mathrm{Joules/bit}]
\end{align}
%
